It was a peaceful Sunday morning.  Lucy rose late and dressed leisurely, having
been assigned to the late morning Mass this Sunday, rather than the early
morning one she preferred.  Going without sleep made her feel abstinent, and
abstinence was, of course, holier.  Ah well.  As her custom was to fast until
she took Communion, she traded her abstinence from sleep for abstinence from
nourishment.  The Lord would accept either, she hoped.

She bathed with sweet-smelling soaps and dressed in a meticulously-pressed
robe.  Long and white with red and gold trim, the simple red cross on the chest
marked her as a journeyman of the Church.  Makeup did not befit an adherent,
but Lucy allowed herself a single concession to adornment and twisted her shiny
hair up into an elegant knot.

Lucy examined herself briefly in the mirror---satisfied that she was ready, she
placed a simple wooden cross on a strand of prayer beads around her neck,
tucked it into her habit, and exited her apartment, stepping into sandals that
had been laid out the night before.

It was a bright morning, so bright that Lucy was momentarily blinded as she
stepped out of her apartment onto the Cathedral's courtyard.  The sounds of
bustling streets filtered in over the outer wall---in addition to being the
seat of the Triumvirate, Neo Vatica was the Empire's premier commerical center,
and the Lord might have rested on the seventh day, but tradesmen did not share
that particular luxury.

Lucy walked slowly along the cobblestone path that ran like a spiderweb through
the immaculate lawn.  Two Paladins in full armor approached from the direction
of the main hall.

"Hello, Paladins!"  Lucy greeted them cheerily with a short wave.

"Hail, Adherent," replied one with a curt nod, the voice filter in his
full-face helmet flattening the humanity out of his voice. "\textit{Laudetur
Jesus Christus}."

"\textit{In saecula saeculorum, amen}," she replied as they parted, allowing
her to pass between them.

Lucy skipped slightly and then decided it didn't befit her dignity to continue,
so she adopted a more regal, stately glide. Who was giving the sermon today?
Was it Father Michael? Hopefully not Father Edward, he was among the greatest
scholars in Christendom, but Lucy swore she'd seen at \textit{least} one of the
Triumviri snoring during one of his sermons.

It was neither. The sermon was given instead by a new priest, Trevor, who had
explained to the congregation that this was his first time at the pulpit and
then proceeded to give the most fiery sermon Lucy had ever heard.

"That the Saracen legions have not been routed is an affront to the Lord our
god!" he shouted, his face reddened and flecks of spit flying. "The Holy Land
is lost to them because they are misguided. Ask yourself why it is lost, then,
to us, when it is we who are upon the truth?"

He paused for a moment and collected himself.

"Ask yourself," he continued in a low, urgent tone. "Ask yourself why we cannot
overcome the Saracens, why we cannot overcome even the metallic beasts that
roam the wastes? We are weak in faith. We are selfish. Who among you would die
for the Empire? Who would spill their own blood in this blessed place if it
meant that the truth would prevail?"

The congregants responded to these exhortations---the priest, who as priests
do, did not retain an iota of his fire and charisma off of the pulpit---was
mobbed by the crowd as he exited. Lucy, by contrast, was unsettled by his
words. Oh, sure, it was fine to carry on living as she did, observing the
laws that the Papal Triumvirate passed down from Heaven. But could she, as
Father Trevor had asked, give everything?

She was not sure.
